---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-"
)
```

# docreview 

<!-- badges: start -->
[![CRAN_Status_Badge](https://www.r-pkg.org/badges/version/docreview)](https://cran.r-project.org/package=docreview)
[![lifecycle](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![R-CMD-check](https://github.com/thisisnic/docreview/workflows/R-CMD-check/badge.svg)](https://github.com/thisisnic/docreview/actions?query=workflow%3AR-CMD-check)
[![codecov](https://codecov.io/gh/thisisnic/docreview/branch/main/graph/badge.svg)](https://codecov.io/gh/thisisnic/docreview)
<!-- badges: end -->

_An opinionated package for enhancing your R package documentation._

When writing R packages, high quality documentation can make for a great experience for your users.  

You can use __docreview__ to check that your R package documentation passes a number of checks:

* all exported functions should have documented examples of how to use them
* vignettes should not be too long
* vignettes should not be too complex

## Installation

```{r, eval=FALSE}
# Install the development version from GitHub:
# install.packages("devtools")
devtools::install_github("thisisnic/docreview")
```

## Usage

```{r, eval=FALSE}
library(docreview)
pkg_path <- system.file("testpkg", package = "docreview")
package_review(path = pkg_path)
```

See [the vignette](https://thisisnic.github.io/docreview/articles/docreview.html) for more detailed usage guides.

## Current default review checks
* Vignettes have no more than 2000 words (warn) or 3000 words (fail)
* Vignettes have no fewer than 100 words (warn) or 0 words (fail)
* Vignettes have a Flesch-Kincaid readability score lower than 50 (warn) or 30 (fail)
* All exported functions have examples in their documentation
