---
title: "Introduction to docreview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{docreview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = ""
)
```

```{r setup, include=FALSE}
devtools::load_all()
```

When writing R packages, high quality documentation can make for a great experience for your users.  

You can use docreview to check that your R package documentation follows a number of rules:

* all exported functions have documented examples of how to use them
* vignettes should not be too long
* vignettes should not be too complex

You can use docreview within your package's CI builds to ensure that these standards are still met as your package evolves.

## Basic usage
```{r}
docreview::package_review(path = system.file("testpkg", package = "docreview"))
```
 
## Choose what to review

You can choose which components of documentation to review.

## Set custom thresholds for review check failures and warnings

You might not agree with the thresholds set for review checks resulting in failures or warnings.  That's OK!  You can set your own custom thresholds.

## Raise an error when review checks produce failures or warnings

If you're using docreview as part of your CI, you may want to raise an error when the review checks produce a failure or warning.

