---
title: "Introduction to docreview"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{docreview}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = ""
)
```

```{r setup, include=FALSE}
devtools::load_all()
```

When writing R packages, high quality documentation can make for a great experience for your users.  

You can use docreview to check that your R package documentation follows a number of rules:

* all exported functions have documented examples of how to use them
* vignettes should not be too long
* vignettes should not be too complex

You can use docreview within your package's CI builds to ensure that these standards are still met as your package evolves.

## Basic usage
```{r}
docreview::package_review(path = system.file("testpkg", package = "docreview"))
```
 
## Choose what to review

## Set custom thresholds for review check failures and warnings

## Raise an error when review checks produce failures or warnings

