---
title: "glossary"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(docreview)
```

# Glossary of docreview terms

* check - an aspect of the documentation that it to be removed, and it's associated attributes

For example, `flesch-kincaid` checks a vignette's readability. Its attributes are:
* `active` - whether this check is currently active or not
* `thresholds` - numerical values corresponding to scores at which this check will fail. These may be divided into subchecks.

```
flesch-kincaid:
    active: true
    thresholds:
      poor_readbility:
        active: true
        warn: 50
        fail: 30
```

* subcheck - a check which has been further divided into subchecks.

For example, `length` checks a vignette's word length.

```
length:
    active: true
    thresholds:
      too_long:
        active: true
        warn: 2000
        fail: 3000
      too_short:
        active: true
        warn: 100
        fail: 0
```

